Shiny App Manuscript Figures: Aquatic Organisms

### 2022-05-03 App_Nonessential/TeamX_Manuscript_Figures/Manuscript_Figures_TeamX.Rmd

#Import packages
library(tidyverse) 
library(wesanderson)
library(pheatmap)
library(RColorBrewer)
library(ggpubr)
library(ssdtools)
library(scales)

library(ggdark)
library(ggsci)

@@

ggsave(filename = "Figure1.jpg",
       path = "App_Nonessential/TeamX_Manuscript_Figures/",
       plot = map, width = 8, height = 4, units = "in")

@@

b <- a %>%
  ggplot(aes(x = year, y = freq, fill = fct_rev(dose_metric))) +
  geom_bar(position = "dodge", stat = "identity", color = "black") +
  theme_classic()+
  scale_fill_manual(values = c('#d73027','#fee090','#4575b4')) +
  scale_y_continuous(expand = c(0,0), limits = c(0,40)) +
  labs(y = "Number of Studies", x = "Year", fill = "Concentration Metric") +
  theme(text = element_text(size = 20), legend.position = "top")

@@

a <- aoc_setup %>% 
  filter(environment != "Terrestrial") %>% #drop terrestrial organisms
  filter(shape_f != "Not Reported") %>% #drop studies where shapes aren't reported
  filter(effect_f != "NA") %>% #drop ECX values
  filter(org_f %in% c("Crustacea", "Fish", "Mollusca")) %>%  #Select relevant organism groups
  filter(lvl2_f %in% c("Growth", "Body Condition", "Development", "Mortality", "Reproduction")) %>% 
  ggplot(aes(y = shape_f, x = dose.particles.mL.master, fill = effect_f)) +
  geom_boxplot(alpha = 0.8) +
  scale_x_log10() +
  labs(y = "Morphology", x = "Particles/mL", fill = "Effect") +
  theme_classic() +
  theme(text = element_text(size = 12))+
  scale_fill_manual(values = c("#fee090", '#4575b4'))

ggsave(filename = "Figure3.jpg",
       path = "App_Nonessential/TeamX_Manuscript_Figures/",
       plot = a, width = 8, height = 4, units = "in")

@@

#Panel A (count)
a <- aoc_setup %>% 
  filter(environment != "Terrestrial") %>% #drop terrestrial organisms
  filter(size_f != "Not Reported") %>% #drop studies where shapes aren't reported
  filter(effect_f != "NA") %>% #drop ECX values
  drop_na(dose.mg.L.master|dose.particles.mL.master) %>%
  ggplot(aes(y = size_f, x = dose.particles.mL.master, fill = effect_f)) +
  geom_boxplot(alpha = 0.8) +
  scale_x_log10() +
  labs(y = "Size Category", x = "Particles/mL", fill = "Effect") +
  theme_classic() +
  theme(text = element_text(size = 12))+
  scale_fill_manual(values = c("#fee090", '#4575b4'))

@@

#Panel B (mass)
b <- aoc_setup %>% 
  filter(environment != "Terrestrial") %>% #drop terrestrial organisms
  filter(size_f != "Not Reported") %>% #drop studies where shapes aren't reported
  filter(effect_f != "NA") %>% #drop ECX values
  drop_na(dose.mg.L.master|dose.particles.mL.master) %>%
  ggplot(aes(y = size_f, x = dose.mg.L.master, fill = effect_f)) +
  geom_boxplot(alpha = 0.8) +
  scale_x_log10() +
  labs(y = "Size Category", x = "µg/mL", fill = "Effect") +
  theme_classic() +
  theme(text = element_text(size = 12))+
  scale_fill_manual(values = c("#fee090", '#4575b4'))

@@

@@

@@

Group_size <- aoc_setup %>% 
  ggplot(aes(x = size.length.um.used.for.conversions, fill = org_f)) +
  geom_histogram(bins = 20, color = "black") +
  scale_fill_manual(values = c('#a50026','#d73027','#f46d43','#fdae61','#fee090','#ffffbf','#e0f3f8','#abd9e9','#74add1','#4575b4','#313695', '#641e16')) +
  ylab("Number of Observations")+
  xlab("Particle Length (µm)") +
  theme_classic() +
  theme(text = element_text(size = 12)) +
  scale_x_log10()+
  labs(fill = "Organism Group")

@@

Endpoint_size <- aoc_setup %>% 
  ggplot(aes(x = size.length.um.used.for.conversions, fill = lvl1_f)) +
  geom_histogram(bins = 20, color = "black") +
  scale_fill_manual(values = c('#d73027','#f46d43','#fdae61','#fee090','#ffffbf','#e0f3f8','#abd9e9','#74add1','#4575b4')) +
  xlab("Particle Length (µm)") +
  ylab("Number of Observations")+
  theme_classic() +
  theme(text = element_text(size = 12)) +
  scale_x_log10()+
  labs(fill = "Endpoint Category")

@@

>>>>

#Import packages
library(tidyverse) 
library(wesanderson)
library(pheatmap)
library(RColorBrewer)
library(ggpubr)
library(ssdtools)
library(scales)
library(DT)
library(ggdark)
library(ggsci)

@@

# ggsave(filename = "Figure1.jpg",
#        path = "App_Nonessential/TeamX_Manuscript_Figures/",
#        plot = map, width = 8, height = 4, units = "in")

@@

b <- a %>%
  ggplot(aes(x = year, y = freq, fill = fct_rev(dose_metric))) +
  geom_bar(stat = "identity", color = "black") +
  theme_classic()+
  scale_fill_manual(values = c('#d73027','#fee090','#4575b4')) +
  scale_y_continuous(expand = c(0,0)) +
  labs(y = "Number of Test Concentrations Reported", x = "Year", fill = "Concentration Metric") +
  theme(text = element_text(size = 20), legend.position = "top")

@@

#Studies and measurements labels
a <- aoc_setup %>% 
      drop_na(dose.particles.mL.master) %>% #Drop data not reported in counts
      drop_na(effect_f) %>% #drop ECX values
      filter(shape_f != "Not Reported") %>% #drop studies where shapes aren't reported
      group_by(shape_f, effect_f) %>% # need to include so there's a recognized "y"
      summarize(dose.particles.mL.master= quantile(dose.particles.mL.master, .1), # need for recognized "x"
                measurements = n(),
                studies = n_distinct(doi))

#Select data
b <- aoc_setup %>%
  drop_na(dose.particles.mL.master) %>%
  filter(environment != "Terrestrial") %>% #drop terrestrial organisms
  filter(shape_f != "Not Reported") %>% #drop studies where shapes aren't reported
  filter(effect_f != "NA") %>% #drop ECX values
  filter(org_f %in% c("Crustacea", "Fish", "Mollusca")) %>%  #Select relevant organism groups
  filter(lvl2_f %in% c("Growth", "Body Condition", "Development", "Mortality", "Reproduction"))

#Plot
c <- b %>% 
  ggplot(aes(y = shape_f, x = dose.particles.mL.master, fill = effect_f)) +
  geom_boxplot(alpha = 0.8) +
  geom_text(data = a, 
                aes(label = paste("(",measurements,",",studies,")"),
                  y = shape_f,
                  x = Inf,
                  hjust = 1),
                position = position_dodge(.9),
                size = 3)+
  scale_x_log10(limits = c(-1,10000000000000000)) +
  labs(y = "Morphology", x = "Particles/mL", fill = "Effect") +
  theme_classic() +
  theme(text = element_text(size = 12))+
  scale_fill_manual(values = c("#fee090", '#4575b4'))

plot(c)

ggsave(filename = "Figure3.jpg",
       path = "App_Nonessential/TeamX_Manuscript_Figures/",
       plot = c, width = 8, height = 4, units = "in")

#Table

d <- b %>%
  select(doi, authors, year, species_f, life_f, shape_f, lvl1_f, lvl2_f, lvl3_f, dose.particles.mL.master, effect_f) %>% 
  rename("DOI" = doi, "Authors" = authors, "Publication Year" = year, 
         "Species" = species_f, "Life Stage" = life_f, "Shape" = shape_f, 
         "Broad Endpoint Category" = lvl1_f, "Specific Endpoint Category" = lvl2_f,
         "Endpoint" = lvl3_f, "Concentration (Particles/mL)" = dose.particles.mL.master, 
         "Effect Detected?" = effect_f)

write.csv(d, "App_Nonessential/TeamX_Manuscript_Figures/Figure3_Data_SI.csv", row.names = FALSE)

@@

#Panel A (count)

#Studies and measurements labels
a_labs <- aoc_setup %>% 
      drop_na(dose.mg.L.master|dose.particles.mL.master) %>%
      drop_na(effect_f) %>% #drop ECX values
      filter(environment != "Terrestrial") %>% #drop terrestrial organisms
      filter(size_f != "Not Reported") %>% #drop studies where shapes aren't reported
      filter(effect_f != "NA") %>% #drop ECX values
      group_by(size_f, effect_f) %>% # need to include so there's a recognized "y"
      summarize(dose.particles.mL.master= quantile(dose.particles.mL.master, .1), # need for recognized "x"
                measurements = n(),
                studies = n_distinct(doi))

a <- aoc_setup %>% 
  filter(environment != "Terrestrial") %>% #drop terrestrial organisms
  filter(size_f != "Not Reported") %>% #drop studies where shapes aren't reported
  filter(effect_f != "NA") %>% #drop ECX values
  drop_na(dose.mg.L.master|dose.particles.mL.master) %>%
  ggplot(aes(y = size_f, x = dose.particles.mL.master, fill = effect_f)) +
  geom_boxplot(alpha = 0.8) +
  geom_text(data = a_labs, 
                aes(label = paste("(",measurements,",",studies,")"),
                  y = size_f,
                  x = Inf,
                  hjust = 1),
                position = position_dodge(.9),
                size = 3)+
  scale_x_log10(limits = c(-1,1E25)) +
  labs(y = "Size Category", x = "Particles/mL", fill = "Effect") +
  theme_classic() +
  theme(text = element_text(size = 12))+
  scale_fill_manual(values = c("#fee090", '#4575b4'))

@@

#Panel B (mass)

#Studies and measurements labels
b_labs <- aoc_setup %>% 
      drop_na(dose.mg.L.master|dose.particles.mL.master) %>%
      drop_na(effect_f) %>% #drop ECX values
      filter(environment != "Terrestrial") %>% #drop terrestrial organisms
      filter(size_f != "Not Reported") %>% #drop studies where shapes aren't reported
      filter(effect_f != "NA") %>% #drop ECX values
      group_by(size_f, effect_f) %>% # need to include so there's a recognized "y"
      summarize(dose.mg.L.master= quantile(dose.mg.L.master, .1), # need for recognized "x"
                measurements = n(),
                studies = n_distinct(doi))

b <- aoc_setup %>% 
  filter(environment != "Terrestrial") %>% #drop terrestrial organisms
  filter(size_f != "Not Reported") %>% #drop studies where shapes aren't reported
  filter(effect_f != "NA") %>% #drop ECX values
  drop_na(dose.mg.L.master|dose.particles.mL.master) %>%
  ggplot(aes(y = size_f, x = dose.mg.L.master, fill = effect_f)) +
  geom_boxplot(alpha = 0.8) +
  geom_text(data = b_labs, 
                aes(label = paste("(",measurements,",",studies,")"),
                  y = size_f,
                  x = Inf,
                  hjust = 1),
                position = position_dodge(.9),
                size = 3)+
  scale_x_log10(limits = c(-1,1E25)) +
  labs(y = "Size Category", x = "µg/mL", fill = "Effect") +
  theme_classic() +
  theme(text = element_text(size = 12))+
  scale_fill_manual(values = c("#fee090", '#4575b4'))

@@

#Table

d <- aoc_setup %>%
  filter(environment != "Terrestrial") %>% #drop terrestrial organisms
  filter(size_f != "Not Reported") %>% #drop studies where shapes aren't reported
  filter(effect_f != "NA") %>% #drop ECX values
  drop_na(dose.mg.L.master|dose.particles.mL.master) %>%
  select(doi, authors, year, species_f, life_f, size_f, lvl1_f, lvl2_f, lvl3_f, 
         dose.particles.mL.master, dose.mg.L.master, effect_f) %>% 
  rename("DOI" = doi, "Authors" = authors, "Publication Year" = year, 
         "Species" = species_f, "Life Stage" = life_f, "Size Category" = size_f, 
         "Broad Endpoint Category" = lvl1_f, "Specific Endpoint Category" = lvl2_f,
         "Endpoint" = lvl3_f, "Concentration (Particles/mL)" = dose.particles.mL.master, 
         "Concentration (µg/mL)" = dose.mg.L.master,
         "Effect Detected?" = effect_f)

write.csv(d, "App_Nonessential/TeamX_Manuscript_Figures/Figure4_Data_SI.csv", row.names = FALSE)

@@

#Data table for export

ssd_table <- aoc_intermediate %>% 
  mutate(dose_filter = ifelse(is.na(dose.particles.mL.master)&is.na(dose.mg.L.master), "N", "Y")) %>% 
  filter(dose_filter == "Y") %>% 
  select(doi, authors, year, species_f, life_f, size_f, lvl1_f, lvl2_f, lvl3_f, 
         dose.particles.mL.master, dose.mg.L.master, effect.metric) %>% 
  rename("DOI" = doi, "Authors" = authors, "Publication Year" = year, 
         "Species" = species_f, "Life Stage" = life_f, "Size Category" = size_f, 
         "Broad Endpoint Category" = lvl1_f, "Specific Endpoint Category" = lvl2_f,
         "Endpoint" = lvl3_f, "Concentration (Particles/mL)" = dose.particles.mL.master, 
         "Concentration (µg/mL)" = dose.mg.L.master, "Effect Metric" = effect.metric)

write.csv(ssd_table, "App_Nonessential/TeamX_Manuscript_Figures/Figure5_Data_SI.csv", row.names = FALSE)

@@

#Group size plot
Group_size <- aoc_setup %>% 
  filter(org_f != "Mixed") %>% 
  filter(size_f != "Not Reported") %>% 
  group_by(org_f, size_f) %>% 
  mutate(count = n()) %>% 
  ungroup() %>% 
  group_by(org_f, size_f, count) %>% 
  summarise() %>% 
  ggplot(aes(x = reorder(org_f, count), y = count, fill = size_f)) +
  geom_col(position = position_stack(reverse = TRUE), color = "black") +
  scale_fill_manual(values = c('#d73027','#fc8d59','#fee090','#e0f3f8','#4575b4')) +
  ylab("Number of Observations")+
  xlab("Organism Group") +
  theme_classic() +
  theme(text = element_text(size = 12),
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  guides(fill = guide_legend(reverse = TRUE))+
  scale_y_continuous(expand = c(0,0))+
  labs(fill = "Size Category")

@@

#Group size table
Group_size_table <- aoc_setup %>%
  filter(org_f != "Mixed") %>% 
  filter(size_f != "Not Reported") %>% 
  group_by(org_f, size_f) %>% 
  mutate(count = n()) %>% 
  ungroup() %>% 
  group_by(org_f, size_f, count) %>% 
  summarise() %>%
  rename("Organism Group" = org_f, "Size Cateogry" = size_f, "Number of Observations" = count)

write.csv(Group_size_table, "App_Nonessential/TeamX_Manuscript_Figures/Figure7A_Data_SI.csv", row.names = FALSE)

#Endpoint size plot
Endpoint_size <- aoc_setup %>%
  mutate(lvl1_f = ifelse(lvl1_f == "Behavioral, Sensory, Neurological", "Behavioral, Neurological", paste(lvl1_f))) %>% 
  filter(size_f != "Not Reported") %>% 
  group_by(lvl1_f, size_f) %>% 
  mutate(count = n()) %>% 
  ungroup() %>% 
  group_by(lvl1_f, size_f, count) %>% 
  summarise() %>% 
  ggplot(aes(x = reorder(lvl1_f, count), y = count, fill = size_f)) +
  geom_col(position = position_stack(reverse = TRUE), color = "black") +
  scale_fill_manual(values = c('#d73027','#fc8d59','#fee090','#e0f3f8','#4575b4')) +
  ylab("Number of Observations")+
  xlab("Endpoint Category") +
  theme_classic() +
  theme(text = element_text(size = 12),
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  guides(fill = guide_legend(reverse = TRUE))+
  scale_y_continuous(expand = c(0,0))+
  labs(fill = "Size Category")+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))

@@

#Endpoint size table
Endpoint_size_table <- aoc_setup %>%
  mutate(lvl1_f = ifelse(lvl1_f == "Behavioral, Sensory, Neurological", "Behavioral, Neurological", paste(lvl1_f))) %>% 
  filter(size_f != "Not Reported") %>% 
  group_by(lvl1_f, size_f) %>% 
  mutate(count = n()) %>% 
  ungroup() %>% 
  group_by(lvl1_f, size_f, count) %>% 
  summarise() %>%
  rename("Endpoint Category" = lvl1_f, "Size Cateogry" = size_f, "Number of Observations" = count)

write.csv(Endpoint_size_table, "App_Nonessential/TeamX_Manuscript_Figures/Figure7B_Data_SI.csv", row.names = FALSE)
